---
title: "2021 QBios Workshop - Building interactive dashboards"
output:
  github_document:
    html_preview: false
author: 
  - Aroon T. Chande  
  - Lavanya Rishishwar
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting started

To get started, clone this repository in the command line or download the ZIP file and open the **`GaTech-QBiosWorkshop-20210518.Rproj`** file with RStudio

```{bash get-files, eval = F}
# clone the repo
git clone git@github.com:appliedbinf/2021-QBiosWorkshop.git
cd 2021-QBiosWorkshop
```

We will also be using RStudio Connect and the [ShinyApps.io](https://www.shinyapps.io/ "shinyapps.io") platform. Please make a free account before the session. You will need your [token](https://www.shinyapps.io/admin/#/tokens) to link RStudio with the ShinyApps.io platform.

## Setting up your environment

### Installing the R dependencies

There are a number of R packages that we will need today to build our dashboards. Please run the below code in your Rstudio console window.

```{r install-deps, eval = F}
packages <- c("shiny", "deSolve")
install.packages(packages)

```

### Linking ShinyApps

To link your [ShinyApps.io](https://www.shinyapps.io/ "shinyapps.io") profile with RStudio, visit your [tokens](https://www.shinyapps.io/admin/#/tokens) page and run the provided code snippet (example below) in your RStudio console.

```{r example-shinyapps-token, eval = F}
rsconnect::setAccountInfo(name = 'appliedbinf',
                          token = 'alongtokenstringhere',
                          secret = 'supersecretsecretstringhere')
```

## Example code

We've provided a series of Shiny code samples in the **`examples`** folder:

```{bash samples, eval = F}
examples/
├── 00_HelloWorld.R
├── 01_HelloSliders.R
├── 02_HelloPlots.R
├── 03_HelloInteractions.R
├── 04_MoreInteractions.R
├── 05_OrganizingUI.R
├── 06_HelloNavbar.R
├── 07_NavBarApp.R
└── 08_SIRModel.R

```

As the file numbers increase, so does the complexity of the application. **`00_HelloWorld.R`** is the simplest Shiny application and prints a simple "Hello World!" example. **`08_SIRModel.R`** is a full fledged SIRD application, but not much has been done to make it pretty or user friendly.
